Quantifying stochastic noise in cultured\\ circadian reporter cells

### 2015-03-17 main_text.tex
adding italics?

\subsection*{{In silico} prediction of small molecule experiments}
A previously published mathematical model of circadian rhythms \cite{Hirota2012} was used to predict the effects on population damping rate from the dose-dependent small molecule experiments.
The parameters used to capture the effects of each small molecule were the same as described previously \cite{St.John2014}.
The model was converted to a stochastic biochemical system and subsequently simulated using StochKit2 \cite{Sanft2011a} (via GillesPy, \url{https://github.com/JohnAbel/gillespy}).
Population-level rhythms were found by taking the average of $1,000$ noninteracting oscillators, starting at identical initial conditions.
The only parameter left unspecified by the deterministic model was the cell volume, $\Omega$, which controlled the amount of noise in the system.
For each $\Omega$, a damped sinusoid was fit to the population-averaged state trajectory. 
An $R^2$ value was calculated for each fit, taking into account all eight state variables.

>>>>

\subsection*{{\itshape In silico} prediction of small molecule experiments}
A previously published mathematical model of circadian rhythms \cite{Hirota2012} was used to predict the effects on population damping rate from the dose-dependent small molecule experiments.
The parameters used to capture the effects of each small molecule were the same as described previously \cite{St.John2014}.
The model was converted to a stochastic biochemical system and subsequently simulated using StochKit2 \cite{Sanft2011a} (via GillesPy, \url{https://github.com/JohnAbel/gillespy}).
Population-level rhythms were found by taking the average of $1,000$ noninteracting oscillators, starting at identical initial conditions.
The only parameter left unspecified by the deterministic model was the cell volume, $\Omega$, which controlled the amount of noise in the system.
For each $\Omega$, a damped sinusoid was fit to the population-averaged state trajectory. 
An $R^2$ value was calculated for each fit, taking into account all eight state variables.
